---
title: "Data Visualisation - 1"
output: html_notebook
---

https://campus-no-cache.datacamp.com/courses/7125/22546?ex=3
Exercise 3. Numerical values
Keep in mind that discrete numeric data can be considered ordinal. Although this is technically true, we usually reserve the term ordinal data for variables belonging to a small number of different groups, with each group having many members.

The height variable could be ordinal if, for example, we report a small number of values such as short, medium, and tall. Let's explore how many unique values are used by the heights varialbe. For this we can use the unique fuction:

```{r}
x <- c(3, 3, 3, 3, 4, 4, 2)
unique(x)
```

Q3 Use the unique and length functions to determine how many unique heights were reported

Soln:

```{r}
library(dslabs)
data(heights)
x <- heights$height
length(unique(x))
# Answer is 139
```

---------------------
Exercise 4. Tables
One of the useful outputs of data visualization is that we can learn about the distribution of variables. For categorical data we can construct this distribution by simply computing the frequency of each unique value. This can be done with the function table. Here is an example:

```{r}
x <- c(3, 3, 3, 3, 4, 4, 2)
table(x)
```

Q4 Use the table function to compute the frequencies of each unique height value. Because we are using the resulting frequency table in a later exercise we want you to save the results into an object and call it tab.

```{r}
library(dslabs)
data(heights)
x <- heights$height
tab <- table(x)
```
--------------------

Exercise 5. Indicator variables
To see why treating the reported heights as an ordinal value is not useful in practice we note how many values are reported only once.

In the previous exercise we computed the variable tab which reports the number of times each unique value appears. For values reported only once tab will be 1. Use logicals and the function sum to count the number of times this happens.

using which() and length() also works

```{r}
library(dslabs)
data(heights)
tab <- table(heights$height)
sum(tab==1)

```

-------------------

Exercise 6. Data types - heights
Since there are a finite number of reported heights and technically the height can be considered ordinal, which of the following is true:
> -It is more effective to consider heights to be numerical given the number of unique values we observe and the fact that if we keep collecting data even more will be observed.
- It is actually preferable to consider heights ordinal since on a computer there are only a finite number of possibilities.
- This is actually a categorical variable: tall, medium or short.
- This is a numerical variable because numbers are used to represent it.

