---
title: "Assessment, Quantile, Percentiles, Boxplots"
output: html_notebook
---

Exercise 1. Vector lengths
When analyzing data it's often important to know the number of measurements you have for each category.
```{r}
library(dslabs)
data(heights)
male <- heights$height[heights$sex=="Male"]
female <- heights$height[heights$sex=="Female"]
length(male)
length(female)
```


Exercise 2. Percentiles
Suppose we can't make a plot and want to compare the distributions side by side. If the number of data points is large, listing all the numbers is inpractical. A more practical approach is to look at the percentiles. We can obtain percentiles using the quantile function like this

library(dslabs)
data(heights)
quantile(heights$height, seq(.01, 0.99, 0.01))

Create two five row vectors showing the 10th, 30th, 50th, 70th, and 90th percentiles for the heights of each sex called these vectors female_percentiles and male_percentiles.
Then create a data frame called df with these two vectors as columns. The column names should be female and male and should appear in that order. As an example consider that if you want a data frame to have column names names and grades, in that order, you do it like this:

```{r}
library(dslabs)
data(heights)
male <- heights$height[heights$sex=="Male"]
female <- heights$height[heights$sex=="Female"]
male_percentiles <- quantile(male, seq(0.1, 0.9, 0.2))
female_percentiles <- quantile(female, seq(0.1, 0.9, 0.2))
df <- data.frame(female = female_percentiles, male = male_percentiles)
str(df)
df
```

